---
title: "Lab5"
author: "Jason Myers"
date: "6/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 

## Task 1

```{r}
getwd()
```

## Task 2

```{r}
mybin=function(iter=100,n=10, p=0.5){
# make a matrix to hold the samples
#initially filled with NA's
sam.mat=matrix(NA,nr=n,nc=iter, byrow=TRUE)
#Make a vector to hold the number of successes in each trial
succ=c()
for( i in 1:iter){
#Fill each column with a new sample
sam.mat[,i]=sample(c(1,0),n,replace=TRUE, prob=c(p,1-p))
#Calculate a statistic from the sample (this case it is the sum)
succ[i]=sum(sam.mat[,i])
}
#Make a table of successes
succ.tab=table(factor(succ,levels=0:n))
#Make a barplot of the proportions
barplot(succ.tab/(iter), col=rainbow(n+1), main="Binomial simulation", xlab="Number of successes")
succ.tab/iter
}
mybin(iter=100,n=10, p=0.7)
mybin(iter=200,n=10, p=0.7)
mybin(iter=500,n=10, p=0.7)
mybin(iter=1000,n=10, p=0.7)
mybin(iter=10000,n=10, p=0.7)
d <- round(dbinom(0:10,10,.7),4)

```
     0      1      2      3      4      5      6      7      8 
0.0000 0.0001 0.0009 0.0099 0.0357 0.1048 0.1986 0.2679 0.2355 
     9     10 \
0.1194 0.0272 \
The table of the follow function is `r d`\

## Task 3
```{r}
d <- rbinom(20, 1, 0.6)
sample(d,size=5, replace=FALSE)
sample(c(1,0),size=5,prob=c(.6,.4), replace=TRUE)
myhyper=function(iter=100,N=20,r=12,n=5){
# make a matrix to hold the samples
#initially filled with NA's
sam.mat=matrix(NA,nr=n,nc=iter, byrow=TRUE)
#Make a vector to hold the number of successes over the trials
succ=c()
for( i in 1:iter){
#Fill each column with a new sample
sam.mat[,i]=sample(rep(c(1,0),c(r,N-r)),n,replace=FALSE)
#Calculate a statistic from the sample (this case it is the sum)
succ[i]=sum(sam.mat[,i])
}
#Make a table of successes
succ.tab=table(factor(succ,levels=0:n))
#Make a barplot of the proportions
barplot(succ.tab/(iter), col=rainbow(n+1), main="HYPERGEOMETRIC simulation", xlab="Number of successes")
succ.tab/iter
}
myhyper(iter=100,n=5, N=20,r=12)
myhyper(iter=200,n=5, N=20,r=12)
myhyper(iter=500,n=5, N=20,r=12)
myhyper(iter=1000,n=5, N=20,r=12)
myhyper(iter=10000,n=5, N=20,r=12)
d <- round(dhyper(x=0:5, m=12, n=8, k=5),4)
```
    0     1     2     3     4     5 \
0.004 0.056 0.249 0.396 0.247 0.048 \
`r d`\

## Task 4

The function creates a sample based on how large the user wants but the spread or range is lock between 1 and 10. Loop through selecting random numbers and store them into a level or bin. Then prints the result to the screen
```{r}
mysample=function(n, iter=10,time=0.5){
  for( i in 1:iter){
    #make a sample
    s=sample(1:10,n,replace=TRUE)
    # turn the sample into a factor
    sf=factor(s,levels=1:10)
    #make a barplot
    barplot(table(sf)/n,beside=TRUE,col=rainbow(10),
            main=paste("Example sample()", " iteration ", i, " n= ", n,sep="") ,
            ylim=c(0,0.2)
    )

    #release the table
    Sys.sleep(time)
  }
}

v <- mysample(n=1000, iter=30, time = 1)
```
The graph show the different number selection during the running of the function. It show mostly and even distrubition over the entire running time


## Task 5

```{r}
v <- choose(8,4)
d <- 1-ppois(3,4)
c <- choose(9,2)*.4^3*.6^(10-3)
q<-dnbinom(x=10-3,size=3,.4)
w <- pnbinom(7,15,.4)
```
The Binomial $\binom{8}{4}$ = `r v`\
P(Y>4),Y~Pois($\lambda$ = 2) = `r d`\
p(Y=10),Y~negBin(p = 0.4, r = 3) = `r c` = `r q`\
p($Y\le 8$), Y~Bin(n=15,p=.4) = `r w`\
